Efficiency

### 2018-01-24 DraftExec.Rnw
added one more ref to AFR

The choice of the pumpjet propulsion system is quite probably the most significant new technology inclusion for Australia's future submarines.  Unlike other modern technolgoies such as Air Independent Propulsion and Lithium Ion Batteries, which are either in service or entering service in multiple other navies, no other navies have have adopted pumpjet technology for their conventional sumbarines, which is currently only used by nuclear submarines.

>>>>

The choice of the pumpjet propulsion system is quite probably the most significant new technology inclusion for Australia's future submarines.  Unlike other modern technolgoies such as Air Independent Propulsion and Lithium Ion Batteries, which are either in service or entering service in multiple other navies, no other navies have have adopted pumpjet technology for their conventional sumbarines, which is currently only used by nuclear submarines \parencite(coorey2016).
